---
title: "PDSI Index"
output: html_notebook
---



```{r}


  library(package = "tidyverse")
  library(package = "tidypredict")

  library(package = "lubridate") # processing dates and time
  library(package = "stringr")


  library(package = "reshape2")  # manipulating data frames
  library(package = "extRemes")  # extreme data analysis
  library(package = "abind")

  library(package = "ncdf4")
  library(package = "ncdf4.helpers")
  
  library(package = "PCICt")
  
```

File Control

```{r}

# File Control

  URL_Root = "http://kyrill.ias.sdsmt.edu:8080/thredds/catalog/LOCA_NGP/climatology/"
  URL_Root = "~/GitHub/PDSI_LOCA/LOCA_Local_Files/LOCA_NGP/climatology/"


```



```{r}
# Ensemble Members

ensembles = c( "ACCESS1-0_r1i1p1",
               "ACCESS1-3_r1i1p1",
               "CCSM4_r6i1p1",
               "CESM1-BGC_r1i1p1",
               "CESM1-CAM5_r1i1p1",
               "CMCC-CMS_r1i1p1",
               "CMCC-CM_r1i1p1",
               "CNRM-CM5_r1i1p1",
               "CSIRO-Mk3-6-0_r1i1p1",
               "CanESM2_r1i1p1",
               "FGOALS-g2_r1i1p1",
               "GFDL-CM3_r1i1p1",
               "GFDL-ESM2G_r1i1p1",
               "GFDL-ESM2M_r1i1p1",
               "HadGEM2-AO_r1i1p1",
               "HadGEM2-CC_r1i1p1",
               "HadGEM2-ES_r1i1p1",
               "IPSL-CM5A-LR_r1i1p1",
               "IPSL-CM5A-MR_r1i1p1",
               "MIROC-ESM_r1i1p1",
               "MIROC5_r1i1p1",
               "MPI-ESM-LR_r1i1p1",
               "MPI-ESM-MR_r1i1p1",
               "MRI-CGCM3_r1i1p1",
               "NorESM1-M_r1i1p1",
               "bcc-csm1-1-m_r1i1p1" )

```

# ${URL_Root}/1950-2005/MONTHLY/pr/LOCA_NGP_pr_ACCESS1-0_r1i1p1_historical_1950-2005_CDO_MONTLY_TOTAL.nc
# ${URL_Root}/${period}/MONTHLY/${var}/LOCA_NGP_${var}_${ens}_${scen}_${period}_${agg}.nc
# ${URL_Root}/${period}/MONTHLY/${var}/LOCA_NGP_${variable}_${period}_${agg}.nc

# Varible Template 
# 
# ${var}_${ens}_${scen}_${period}

# URL Template
#
# ${URL_Root}/${period}/MONTHLY/${var}/LOCA_NGP_${variable}_${period}_${agg}.nc



```{r}

# extract the time series information.
#


ens  = ensembles[1]


  var = "pr"
  agg = "CDO_MONTLY_TOTAL"


  # historical time information

  scen   = "historical"
  period = "1950-2005"
  
  variable = str_c(var,
                   ens,
                   scen,
                   sep = "_")
  
  
  URL_Name = str_c(URL_Root,
                   period,
                   "/MONTHLY/",
                   var,
                   "/LOCA_NGP_",
                   variable,
                   "_",
                   period,
                   "_",
                   agg,
                   ".nc",
                   sep = "")
  
  
  ncf = nc_open(filename = URL_Name)
  
    longitude        = ncvar_get(nc           = ncf, 
                                 varid        = "lon", 
                                 verbose      = FALSE,
                                 raw_datavals = FALSE )
  
    latitude         = ncvar_get(nc           = ncf, 
                                 varid        = "lat", 
                                 verbose      = FALSE,
                                 raw_datavals = FALSE )  
    
    longitude_bounds = ncvar_get(nc           = ncf, 
                                 varid        = "lon_bnds", 
                                 verbose      = FALSE,
                                 raw_datavals = FALSE )
      
    
    latitude_bounds =  ncvar_get(nc           = ncf, 
                                 varid        = "lat_bnds", 
                                 verbose      = FALSE,
                                 raw_datavals = FALSE )      
    
    time_historial  = nc.get.time.series(f                            = ncf, 
                                         v                            = variable, 
                                         time.dim.name                = "time", 
                                         correct.for.gregorian.julian = FALSE, 
                                         return.bounds                = FALSE)
    
    time_historial = as.POSIXct(x  = time_historial)
    
  remove(ncf)
  
  
  # future time information

  scen   = "rcp85"
  period = "2006-2099"
  
  variable = str_c(var,
                   ens,
                   scen,
                   sep = "_")
  
  
  URL_Name = str_c(URL_Root,
                   period,
                   "/MONTHLY/",
                   var,
                   "/LOCA_NGP_",
                   variable,
                   "_",
                   period,
                   "_",
                   agg,
                   ".nc",
                   sep = "")
  
  
  ncf = nc_open(filename = URL_Name)
  
    time_futr = nc.get.time.series(f                            = ncf, 
                                   v                            = variable, 
                                   time.dim.name                = "time", 
                                   correct.for.gregorian.julian = FALSE, 
                                   return.bounds                = FALSE)
    
    time_futr = as.POSIXct(x  = time_futr)
    
  remove(ncf)    
  
  time = as.POSIXct(x      = abind(time_historial,
                                   time_futr),
                    origin = "1970-01-01 00:00:00 UTC", 
                    tz     = "UTC")
  
  t0h = 1
  t9h = length(time_historial)
  
  t0f = t9h + 1
  t9f = length(time)   
  
  print("Time Limits")
  print(time[t0h])
  print(time[t9h])
  print(time[t0f])
  print(time[t0f])

```


Replication Prototyping Goes Here

```{r}

target_lon =  -101.5988405
target_lat =    44.0487306

i_targ = which(abs(longitude - target_lon) == min(abs(longitude - target_lon)))
j_targ = which(abs(latitude  - target_lat) == min(abs(latitude  - target_lat)))




```


Extract data fields

```{r}

ens = ensembles[1]



  # Historicals

  scen   = "historical"
  period = "1950-2005"
  
    # Precip
    
    var = "pr"
    agg = "CDO_MONTLY_TOTAL"
    
    variable = str_c(var,
                     ens,
                     scen,
                     sep = "_")
    
    URL_Name = str_c(URL_Root,
                     period,
                     "/MONTHLY/",
                     var,
                     "/LOCA_NGP_",
                     variable,
                     "_",
                     period,
                     "_",
                     agg,
                     ".nc",
                     sep = "")
    
    nc_f = nc_open(filename = URL_Name)
  
    pr_hist_xyt = ncvar_get(nc           = nc_f,
                         varid        = variable,
                         verbose      = FALSE,
                         raw_datavals = FALSE)
    
 
    # Max T
    
    var = "tasmax"
    agg = "CDO_MONTLY_MEAN"
    
    variable = str_c(var,
                     ens,
                     scen,
                     sep = "_")
    
    URL_Name = str_c(URL_Root,
                     period,
                     "/MONTHLY/",
                     var,
                     "/LOCA_NGP_",
                     variable,
                     "_",
                     period,
                     "_",
                     agg,
                     ".nc",
                     sep = "")
    
    nc_f = nc_open(filename = URL_Name)
  
    tasmax_hist_xyt = ncvar_get(nc           = nc_f,
                         varid        = variable,
                         verbose      = FALSE,
                         raw_datavals = FALSE)
    
 
    # Min T
    
    var = "tasmin"
    agg = "CDO_MONTLY_MEAN"
    
    variable = str_c(var,
                     ens,
                     scen,
                     sep = "_")
    
    URL_Name = str_c(URL_Root,
                     period,
                     "/MONTHLY/",
                     var,
                     "/LOCA_NGP_",
                     variable,
                     "_",
                     period,
                     "_",
                     agg,
                     ".nc",
                     sep = "")
    
    nc_f = nc_open(filename = URL_Name)
  
    tasmin_hist_xyt = ncvar_get(nc           = nc_f,
                         varid        = variable,
                         verbose      = FALSE,
                         raw_datavals = FALSE)    
    
    
    

  # RCP 8.5

  scen   = "rcp85"
  period = "2006-2099"
  
    # Precip
    
    var = "pr"
    agg = "CDO_MONTLY_TOTAL"
    
    variable = str_c(var,
                     ens,
                     scen,
                     sep = "_")
    
    URL_Name = str_c(URL_Root,
                     period,
                     "/MONTHLY/",
                     var,
                     "/LOCA_NGP_",
                     variable,
                     "_",
                     period,
                     "_",
                     agg,
                     ".nc",
                     sep = "")
    
    nc_f = nc_open(filename = URL_Name)
  
    pr_rcp85_xyt = ncvar_get(nc       = nc_f,
                         varid        = variable,
                         verbose      = FALSE,
                         raw_datavals = FALSE)
    
 
    # Max T
    
    var = "tasmax"
    agg = "CDO_MONTLY_MEAN"
    
    variable = str_c(var,
                     ens,
                     scen,
                     sep = "_")
    
    URL_Name = str_c(URL_Root,
                     period,
                     "/MONTHLY/",
                     var,
                     "/LOCA_NGP_",
                     variable,
                     "_",
                     period,
                     "_",
                     agg,
                     ".nc",
                     sep = "")
    
    nc_f = nc_open(filename = URL_Name)
  
    tasmax_rcp85_xyt = ncvar_get(nc           = nc_f,
                         varid        = variable,
                         verbose      = FALSE,
                         raw_datavals = FALSE)
    
 
    # Min T
    
    var = "tasmin"
    agg = "CDO_MONTLY_MEAN"
    
    variable = str_c(var,
                     ens,
                     scen,
                     sep = "_")
    
    URL_Name = str_c(URL_Root,
                     period,
                     "/MONTHLY/",
                     var,
                     "/LOCA_NGP_",
                     variable,
                     "_",
                     period,
                     "_",
                     agg,
                     ".nc",
                     sep = "")
    
    nc_f = nc_open(filename = URL_Name)
  
    tasmin_rcp85_xyt = ncvar_get(nc           = nc_f,
                                 varid        = variable,
                                 verbose      = FALSE,
                                 raw_datavals = FALSE)    


  # RCP 4.5

  scen   = "rcp45"
  period = "2006-2099"
  
    # Precip
    
    var = "pr"
    agg = "CDO_MONTLY_TOTAL"
    
    variable = str_c(var,
                     ens,
                     scen,
                     sep = "_")
    
    URL_Name = str_c(URL_Root,
                     period,
                     "/MONTHLY/",
                     var,
                     "/LOCA_NGP_",
                     variable,
                     "_",
                     period,
                     "_",
                     agg,
                     ".nc",
                     sep = "")
    
    nc_f = nc_open(filename = URL_Name)
  
    pr_rcp45_xyt = ncvar_get(nc           = nc_f,
                             varid        = variable,
                             verbose      = FALSE,
                             raw_datavals = FALSE)
    
 
    # Max T
    
    var = "tasmax"
    agg = "CDO_MONTLY_MEAN"
    
    variable = str_c(var,
                     ens,
                     scen,
                     sep = "_")
    
    URL_Name = str_c(URL_Root,
                     period,
                     "/MONTHLY/",
                     var,
                     "/LOCA_NGP_",
                     variable,
                     "_",
                     period,
                     "_",
                     agg,
                     ".nc",
                     sep = "")
    
    nc_f = nc_open(filename = URL_Name)
  
    tasmax_rcp45_xyt = ncvar_get(nc           = nc_f,
                                 varid        = variable,
                                 verbose      = FALSE,
                                 raw_datavals = FALSE)
     
 
    # Min T
    
    var = "tasmin"
    agg = "CDO_MONTLY_MEAN"
    
    variable = str_c(var,
                     ens,
                     scen,
                     sep = "_")
    
    URL_Name = str_c(URL_Root,
                     period,
                     "/MONTHLY/",
                     var,
                     "/LOCA_NGP_",
                     variable,
                     "_",
                     period,
                     "_",
                     agg,
                     ".nc",
                     sep = "")
    
    nc_f = nc_open(filename = URL_Name)
  
    tasmin_rcp45_xyt = ncvar_get(nc           = nc_f,
                                 varid        = variable,
                                 verbose      = FALSE,
                                raw_datavals = FALSE)    
    
    remove(nc_f)
    
    dimnames(tasmin_hist_xyt)  = list("longitude" = longitude,
                                      "latitude"  = latitude,
                                      "Time"      = time_historial)
    
    dimnames(tasmin_rcp45_xyt) = list("longitude" = longitude,
                                      "latitude"  = latitude,
                                      "Time"      = time_futr)

    dimnames(tasmin_rcp85_xyt) = list("longitude" = longitude,
                                      "latitude"  = latitude,
                                      "Time"      = time_futr)    
    
    dimnames(tasmax_hist_xyt)  = list("longitude" = longitude,
                                      "latitude"  = latitude,
                                      "Time"      = time_historial)
    
    dimnames(tasmax_rcp45_xyt) = list("longitude" = longitude,
                                      "latitude"  = latitude,
                                      "Time"      = time_futr)

    dimnames(tasmax_rcp85_xyt) = list("longitude" = longitude,
                                      "latitude"  = latitude,
                                      "Time"      = time_futr)        

    
    dimnames(pr_hist_xyt)  = list("longitude" = longitude,
                                  "latitude"  = latitude,
                                  "Time"      = time_historial)
    
    dimnames(pr_rcp45_xyt) = list("longitude" = longitude,
                                  "latitude"  = latitude,
                                  "Time"      = time_futr)

    dimnames(pr_rcp85_xyt) = list("longitude" = longitude,
                                  "latitude"  = latitude,
                                  "Time"      = time_futr)   
    
    
    output_file = str_c("./LOCA_NGP_",
                        "allvars_",
                        ens,
                        "_allscenarios_MONTHLY.Rdata",
                        sep(""))
                        
    ensemble = ens
    save(ensemble,
         time,
         time_historial,
         time_futr,
         longitude,
         latitude,
         pr_hist_xyt,
         tasmin_hist_xyt,
         tasmax_hist_xyt,
         pr_rcp45_xyt,
         tasmin_rcp45_xyt,
         tasmax_rcp45_xyt,
         pr_rcp85_xyt,
         tasmin_rcp85_xyt,
         tasmax_rcp85_xyt,
         file = output_file)
    
    

```

